%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\usepackage{graphicx}
\input{glyphtounicode}

% \definecolor{customBlue}{RGB}{163, 8, 47}
\definecolor{customBlue}{RGB}{ 37, 82, 143}
% \definecolor{customBlue}{RGB}{ 0, 0, 0}
\definecolor{customGrey}{RGB}{0, 0, 0}
%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small{#2} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}



\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small#2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    {\color{customBlue}\sffamily\fontsize{30pt}{96pt}\selectfont {KHUSHI BUDHWAR}} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:6479632342}{(647)-963-2342}
    {$|$}
    \faEnvelope \hspace{.5pt} \href{mailto:kbudhwar@uwaterloo.ca}{kbudhwar@uwaterloo.ca}
    {$|$}
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/khushi-budhwar/}{khushi-budhwar}
    {$|$}
    \scalebox{1.15}{\faGithub} \href{https://github.com/kbudhwar}{kbudhwar}
    {$|$}
    \scalebox{1.1}{\faGlobe}  \href{https://khushibudhwar.ca/}{khushibudhwar.ca}
\end{center}

%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\color{customBlue} {University of Waterloo} \color{black} $|$ \small{Bachelor of Software} Engineering
      }{Sep 2021 \textbf{--} April 2026}
    \resumeItemListStart
        \resumeItem {\textbf{Relevant Coursework: }Data Structures and Algorithms, Object-Oriented Programming, compilers, and statistics.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Languages:}{ Python, SQL, R, Java, C, C++, C\#, JavaScript, Bash, HTML, CSS, PHP, MATLAB} \\ \vspace{3pt}
        
        \textbf{Frameworks/Libraries:}{ PyTorch, TensorFlow, Scikit-Learn, Spark, Keras, Pandas, NumPy} \\ \vspace{3pt}
        \textbf{Tools:}{ Kubernetes, MLflow, Terraform, GCP, Docker, Git, Tableau, Apache Airflow, Jenkins, BigQuery} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd

%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\color{customBlue}Spotify  \color{black} $|$ \small{Product Data Science Intern}}{May 2024 \textbf{--} July 2024}
        \resumeItemListStart
            \resumeItem{Researched proprio}
            \resumeItem{}
            \resumeItem{}
        \resumeItemListEnd

    \resumeSubheading
      {\color{customBlue} Arami Lab \color{black} $|$ \small{Undergraduate Research Assistant}}{Jan 2024 \textbf{--} Aug 2024}
        \resumeItemListStart
            \resumeItem{Conducted and authored research on proprioception using statistical modeling of \textbf{70,000+} rows of EMG and kinematics data from BURT robots (publication pending).}
            \resumeItem{Performed}
        \resumeItemListEnd
        
    \resumeSubheading
      {\color{customBlue} AltaML \color{black} $|$ \small{Machine Learning Associate}}{Sept 2023 \textbf{--} Dec 2023}
        \resumeItemListStart
            \resumeItem{Developed a time-series forecasting experiment for the Government of Canada to predict current economic trends (nowcasting) in the labor market, achieving a MAPE of \textbf{8\%}.}
            \resumeItem{Performed feature engineering through sentiment analysis on \textbf{10,000+} online job postings and market statistics.}
            \resumeItem{Automated the software development workflow by developing a CI/CD pipeline in GitLab with Jenkins and Docker.}
        \resumeItemListEnd

    \resumeSubheading
      {\color{customBlue} Blackberry \color{black} $|$ \small{Machine Learning Intern}}{Jan 2023 \textbf{--} April 2023}
        \resumeItemListStart
            \resumeItem{Conducted an NLP classification experiment with an F1 score of \textbf{98\%} on imbalanced data to identify open-source licenses in code comments using Pytorch and Tensorflow.}
            \resumeItem{Designed a MySQL schema to extract, preprocess, and store \textbf{130,000+} code comments, easing data processing.}
            \resumeItem{Developed an ML workflow using MLflow, Terraform, and Airflow to automate and track experiments.}
        \resumeItemListEnd

    % \vspace{20pt}
    \resumeSubheading
      {\color{customBlue} VerticalScope Inc. \color{black} $|$ \small{Software Engineering Intern}}{May 2022 \textbf{--} Aug 2022}
        \resumeItemListStart
            \resumeItem{Responsible for the maintenance of a Kubernetes cluster hosted in GCP that serves \textbf{1,200+} community-driven forum sites that receive over \textbf{1 billion} requests weekly.}
        \resumeItemListEnd

    
  \resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\color{customBlue}\textbf{NLP Next Word Predictor } \color{black} \href{https://github.com/kbudhwar}{\scalebox{1.15}{\faGithub}} \hspace{0.5pt} $|$ \textit{\small{ NLTK, TensorFlow, PyTorch}}}{April 2023}
          \resumeItemListStart
            \resumeItem{Constructed an LSTM model that can predict the next word by providing customized lengths of context.}
            \resumeItem{Experimented with NLP models like BiLSTM, BERT, and GRUs using PyTorch to improve accuracy.}
          \resumeItemListEnd
        \resumeProjectHeading
        {\color{customBlue}\textbf{TextSaver}}{Sept 2019 \textbf{--} Nov 2021}
          \resumeItemListStart
            \resumeItem{Founded an all women team to create a web app that condenses a page from a student’s textbook into flashcards.}
            \resumeItem{Viewed in over 50 countries, has collected over \textbf{1,100} emails, and has gained over \textbf{\$1000} from angel investors.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd

\end{document}
